Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-31 algorithm.tex
AA: during the answer revision

\comment{CHECK AND: Per caso era where invece di when ? o manca qualcosa ?}
To summarize,thanks to the above characteristics, PS is able to recognize the regions when the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.

>>>>

To summarize, thanks to the above characteristics, PS is able to recognize the regions where the best configurations are, while avoiding premature convergence, not being trapped in a narrow subset of configuration space.
